Report on a Safety Checker for Petri nets

### 2014-01-30 paper/workspace/main.tex
Formatted example for safety.

The method Safety checks that a given Petri net \verb=N= never violates a property \verb=P=.
We present the method Safety by example on Lamport's 1-bit algorithm by Esparza1997.

@@

\begin{verbatim}
* Property: P = ( cs1 + cs2 >= 1 )
\end{verbatim}

@@

    id1     = 1    + u1    - u2
    ^         ^      |       |
    |         |      |       |
    |         |      |       |
    |         |      |       |
    |         |      |     # of tokens taken from nc
    |         |      |    
    |         |    # of tokens given to nc
    |         |
    |      initial number of tokens in nc
    |
    number of tokens in nc

    cs1 = 0 - u1 + u3
    idle1 = 1 + u1 - u2
    req1 = 0 + u2 - u3
    nid1 = 0 - u1 u2
    id2 = 1 + v2 + v5 - v6
    cs2 = 0 + v4 - v5
    idle2 = 1 + v3 + v5 - v6
    req2 = 0 - v1 - v4 + v6
    after_you2 = 0 + v1 - v2
    await2 = 0 + v2 - v3

    id1 >= 0
    cs1 >= 0
    idle1 >= 0
    req1 >= 0
    nid1 >= 0
    id2 >= 0
    cs2 >= 0
    idle2 >= 0
    req2 >= 0
    after_you2 >= 0
    await2 >= 0
    u1 >= 0
    u2 >= 0
    u3 >= 0
    v1 >= 0
    v2 >= 0
    v3 >= 0
    v4 >= 0
    v5 >= 0
    v6 >= 0
\end{verbatim}

\newpage
\begin{verbatim}
* Place equation:

>>>>

The method Safety checks that a given Petri net \verb=N= never violates a property \verb=P=.
We present the method Safety by example on Lamport's 1-bit algorithm [Esparza1997].

@@

\begin{verbatim}
* Property P: cs1 + cs2 <= 1
\end{verbatim}

@@

    id1        = 1 + u1 - u2
    ^            ^   ^    ^
    |            |   |    |
    |            |   |    |
    |            |   |    |
    |            |   |   # of tokens taken from nc
    |            |   |    
    |            |  # of tokens given to nc
    |            |
    |          initial number of tokens in nc
    |
    number of tokens in nc

    cs1        = 0 - u1      + u3
    idle1      = 1 + u1 - u2
    req1       = 0      + u2 - u3
    nid1       = 0 - u1 + u2
    id2        = 1                     + v2           + v5 - v6
    cs2        = 0                               + v4 - v5
    idle2      = 1                          + v3 + v5 - v6
    req2       = 0                - v1           - v4 + v6
    after_you2 = 0                + v1 - v2
    await2     = 0                     + v2 - v3
\end{verbatim}

\begin{verbatim}
    Non-negativity conditions:

    id1        >= 0
    cs1        >= 0
    idle1      >= 0
    req1       >= 0
    nid1       >= 0
    id2        >= 0
    cs2        >= 0
    idle2      >= 0
    req2       >= 0
    after_you2 >= 0
    await2     >= 0
    u1         >= 0
    u2         >= 0
    u3         >= 0
    v1         >= 0
    v2         >= 0
    v3         >= 0
    v4         >= 0
    v5         >= 0
    v6         >= 0

* Place equation:
